---
title: "Cleaning Notebook V2"
output: html_notebook
---

#############################
*Notebook to clean text data*
#############################

Need to clean text data for topic modeling analysis. Data acquired from transcribed interviews.


#######
*Setup*
#######

Install and load packages and select files for use (Local)

```{r}
#Opening Final Clean XLS
  library(readxl)
  dat.org <- read_xlsx("../../../Desktop/2.13 ARI Text.xlsx")
  dat <- dat.org
  
```

```{r}
# Install and load packages
#install.packages("tm")
#install.packages("utf8")
#install.packages("textclean")
library("utf8")
library("tm")
library("textclean")

# Choose file with a column of text to clean and load it in
#the_file <- choose.files()
#original_dat <- read.csv(the_file)
#colnames(original_dat)
```

#Creating New Column to Start Cleaning
```{r}
# Create and initialize new column to output our clean text to
dat$clean_text <- dat$Segment
dat$clean_text[290]
```

##########################
*Removing Some Punctuation*
##########################
#Replace non-ascii characters
```{r}
dat$clean_text <- lapply(dat$clean_text, replace_non_ascii) # Change non-ascii characters like curly quote
dat$clean_text[290]
```


#Remove all words inside [...]
```{r}
dat$clean_text <- gsub("\\[[^\\]]*\\]", " ", dat$clean_text, perl=TRUE, ignore.case=T)
dat$clean_text[c(1,2,3)]
```

#Remove \
```{r}
dat$clean_text <- gsub("\"", " ", dat$clean_text, perl=TRUE, ignore.case=T)
dat$clean_text[c(25:30)]
```

#Remove all words inside (...)
```{r}
dat$clean_text <- gsub("\\([^\\]]*\\)", " ", dat$clean_text, perl=TRUE, ignore.case=T)
dat$clean_text[203:206]

```

#########################
*Replacing Grammar Stuff*
#########################

# Replace the dashes in the text with a space (yes these are 3 DIFFERENT dashes)
```{r}
dat$clean_text <- gsub('—',' ', dat$clean_text) #Remove the long dashes
dat$clean_text <- gsub('–',' ', dat$clean_text) #Remove the dashes
dat$clean_text <- gsub('-',' ', dat$clean_text) #Remove the dashes

dat$clean_text[203:205]
```

# Replacing Contractions
```{r}
dat$clean_text <- lapply(dat$clean_text, replace_contraction) # Remove contractions
dat$clean_text[204:206]

```

#####################
*Remove MAXQDA Stuff*
#####################

#Interviewee
```{r}
dat$clean_text <- gsub("Female interviewee", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("emale interviewee", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("male interviewee", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("ale interviewee", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("le interviewee", " ", dat$clean_text, ignore.case=T)

#Remove those tricky "Interviewee"s that pop up
dat$clean_text <- gsub('Interviewee:', ' ', dat$clean_text, ignore.case = TRUE)

#Word
dat$clean_text <- gsub("Interviewee", " ", dat$clean_text, ignore.case = TRUE)
```

#nterviewee
```{r}
dat$clean_text <- gsub("Female nterviewee", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("emale nterviewee", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("male nterviewee", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("ale nterviewee", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("le nterviewee", " ", dat$clean_text, ignore.case=T)

#Remove those tricky "Interviewee"s that pop up
dat$clean_text <- gsub('nterviewee:', ' ', dat$clean_text, ignore.case = TRUE)

#Word
dat$clean_text <- gsub("nterviewee", " ", dat$clean_text, ignore.case = TRUE)
```

#erviewee
```{r}
dat$clean_text <- gsub("Female erviewee", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("emale erviewee", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("male erviewee", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("ale erviewee", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("le erviewee", " ", dat$clean_text, ignore.case=T)

#Remove those tricky "Interviewee"s that pop up
dat$clean_text <- gsub('erviewee:', ' ', dat$clean_text, ignore.case = TRUE)

#Word
dat$clean_text <- gsub("erviewee", " ", dat$clean_text, ignore.case = TRUE)
```

#Respondent
```{r}
dat$clean_text <- gsub("Female respondent", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("emale respondent", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("male respondent", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("ale respondent", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("le respondent", " ", dat$clean_text, ignore.case=T)

#Remove those tricky "Interviewee"s that pop up
dat$clean_text <- gsub('Respondent:', ' ', dat$clean_text, ignore.case = TRUE)

#Word
dat$clean_text <- gsub("Respondent", " ", dat$clean_text, ignore.case = TRUE)
```

#Participant
```{r}
dat$clean_text <- gsub("Female participant", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("emale participant", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("male participant", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("ale participant", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("le participant", " ", dat$clean_text, ignore.case=T)

#Word
dat$clean_text <- gsub("participant", " ", dat$clean_text, ignore.case = TRUE)

```

#Speaker
```{r}
dat$clean_text <- gsub("Female speaker", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("emale speaker", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("male speaker", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("ale speaker", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("le speaker", " ", dat$clean_text, ignore.case=T)


#Word
dat$clean_text <- gsub("Speaker", " ", dat$clean_text, ignore.case = TRUE)
```

#Numbers specific to Speaker
```{r}
dat$clean_text <- gsub("1:", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("2:", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("3:", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("4:", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("5:", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("6:", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("7:", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("8:", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("9:", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("0:", " ", dat$clean_text, ignore.case=T)

```

#Colon not followed by a digit (keep time stamps)
```{r}
dat$clean_text <- gsub(":(?!\\d)", " ", dat$clean_text, perl = TRUE, ignore.case=T)
```

####################################
*Remove Verbal Stop Words (Not NLP)*
####################################

#mhmm
```{r}
dat$clean_text <- gsub("\\bmhmmmmm\\.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bmhmmmm\\.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bmhmmm\\.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bmhmm\\.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bmhm\\.\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\bmhmmmmm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bmhmmmm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bmhmmm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bmhmm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bmhm,\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\bmhmmmmm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bmhmmmm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bmhmmm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bmhmm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bmhm\\b", "", dat$clean_text, ignore.case=T)
```

#hmm
```{r}
dat$clean_text <- gsub("\\bhmmmmm\\.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bhmmmm\\.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bhmmm\\.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bhmm\\.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bhm\\.\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\bhmmmmm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bhmmmm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bhmmm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bhmm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bhm,\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\bhmmmmm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bhmmmm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bhmmm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bhmm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bhm\\b", "", dat$clean_text, ignore.case=T)
```

#umm
```{r}
dat$clean_text <- gsub("\\bummmmm\\.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bummmm\\.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bummm\\.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bumm\\.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bum\\.\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\bummmmm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bummmm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bummm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bumm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bum,\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\bummmmm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bummmm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bummm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bumm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bum\\b", "", dat$clean_text, ignore.case=T)
```

#mm
```{r}
dat$clean_text <- gsub("\\bmmm\\.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bmm\\.\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\bmmm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bmm,\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\bmmm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bmm\\b", "", dat$clean_text, ignore.case=T)
```

#ah
```{r}
dat$clean_text <- gsub("\\bahhhhh\\.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bahhhh\\.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bahhh\\.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bahh\\.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bah\\.\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\bahhhhh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bahhhh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bahhh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bahh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bah,\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\bahhhhh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bahhhh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bahhh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bahh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bah\\b", "", dat$clean_text, ignore.case=T)
```

#Uh
```{r}
dat$clean_text <- gsub("\\buhhhhh\\.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\buhhhh\\.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\buhhh\\.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\buhh\\.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\buh\\.\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\buhhhhh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\buhhhh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\buhhh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\buhh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\buh,\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\buhhhhh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\buhhhh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\buhhh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\buhh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\buh\\b", "", dat$clean_text, ignore.case=T)
```

#oh
```{r}
dat$clean_text <- gsub("\\bohhhhh\\.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bohhhh\\.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bohhh\\.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bohh\\.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\boh\\.\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\bohhhhh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bohhhh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bohhh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bohh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\boh,\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\bohhhhh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bohhhh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bohhh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bohh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\boh\\b", "", dat$clean_text, ignore.case=T)
```

#############
*Changing -in' to ing*
#############

```{r}
dat$clean_text <- gsub("\\btalkin'\\b", "talking", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bthinkin'\\b", "thinking", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bcomin'\\b", "coming", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bnothin'\\b", "nothin", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bmissin'\\b", "missing", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bem'\\b", "them", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bdrinkin'\\b", "drinking", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bdoin'\\b", "doing", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bfraternizin'\\b", "fraternizing", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\baskin'\\b", "asking", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bworkin'\\b", "working", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bmakin'\\b", "making", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bshowin'\\b", "showing", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bhurtin'\\b", "hurting", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bkinda\\b", "kind of", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bsayin'\\b", "saying", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\byellin'\\b", "yelling", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bwakin'\\b", "waking", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bscreamin'\\b", "screaming", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bgettin'\\b", "getting", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bwoulda\\b", "would have", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bfloatin'\\b", "floating", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bwanna\\b", "want to", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\btryin'\\b", "trying", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bfrickin'\\b", "fricking", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\blookin'\\b", "looking", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bwatchin'\\b", "watching", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\cuz\\b", "because", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\benforcin'\\b", "enforcing", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\btalkie\\b", "talking", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bhelpin'\\b", "helping", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\b'til\\b", "until", dat$clean_text, ignore.case=T)
```

#############
*Wrapping-Up*
#############

#Remove Commas that are not followed by digits
```{r}
dat$clean_text <- gsub(",(?!\\d)", " ", perl = TRUE, dat$clean_text)
dat$clean_text[405]
```

#Remove apostrophes
```{r}
dat$clean_text <- gsub("'", " ", perl = TRUE, dat$clean_text)
dat$clean_text[405]
```

#Remove the " . "
```{r}
dat$clean_text <- gsub("\\s\\.\\s", " ", dat$clean_text)
dat$clean_text[352]
dat$clean_text[78]
```

#Remove the "..."
```{r}
dat$clean_text <- gsub("\\.\\.\\.", " ", dat$clean_text)
dat$clean_text[352]
dat$clean_text[76]
```

#Remove single-letter words expect "i" and "a" (stray letters from stuttering)
```{r}
dat$clean_text <- gsub("\\b[^ia]\\b", " ", dat$clean_text, ignore.case = TRUE)
dat$clean_text[190]
```

#Remove Spaces
```{r}
dat$clean_text <- gsub("\\s+", " ", dat$clean_text)
dat$clean_text[350]
dat$clean_text[78]
```

#Remove Space at Beginning
```{r}
dat$clean_text <- gsub("^\\s", "", dat$clean_text)
dat$clean_text[350]
dat$clean_text[78]
```

###############
*Output to CSV*
###############

#Step 1 - Removing Normal Parts
```{r}
write.csv(dat, "2.13 ARI Cleaned Data (Step 1).csv")
```


#Step 2 - Removing Like & Just Words
```{r}
#Like
dat$clean_text <- gsub("\\bLike\\.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bLike,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bLike\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\blike\\.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\blike,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\blike\\b", "", dat$clean_text, ignore.case=T)


#Just
dat$clean_text <- gsub("\\bJust\\.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bJust,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bJust\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\bjust\\.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bjust,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\bjust\\b", "", dat$clean_text, ignore.case=T)
```

```{r}
write.csv(dat, "2.13 ARI Cleaned Data (Step 2).csv")
```

### Explore the text 

```{r}
# Use tm package to create a corpus and explore the terms kept
corpus <- Corpus(VectorSource(dat$clean_text))
dtm <- DocumentTermMatrix(corpus)
tdm <- TermDocumentMatrix(corpus)

# Optionally remove terms that appear in <= 1% of documents
#tdm <- removeSparseTerms(tdm, .99)

# Looking at the 100 most frequent words
writeLines("~~~~~~~~~~ Most Frequent Terms ~~~~~~~~~~")
tdm$dimnames$Terms[1:100]

# Looking at the 100 least frequent words
writeLines("\n~~~~~~~~~~ Least Frequent Terms ~~~~~~~~~~")
tdm$dimnames$Terms[(tdm$nrow-100):tdm$nrow]
```


##########################################
#########################################
*Ignore (Jordan's NLP Code will do this)*

- The code I run references some widely used NLP package (I'm pretty sure)

#########################################
#########################################

# Read in our project-specific stop words list
stop_words_file <- choose.files() # Select "StopWordList-ARI Project.txt"
our_stop_words <- readLines(stop_words_file) # Read it in


# Remove some extra punctuation and formatting
dat$clean_text <- gsub('[[:punct:]]', ' ', dat$clean_text) # Remove punctuation
dat$clean_text <- gsub('…',' ', dat$clean_text) # Remove the fancy ellipses
#dat$clean_text <- removeNumbers(dat$clean_text) # Remove numbers

dat$clean_text <- stringr::str_replace_all(dat$clean_text, stop_words_regex, '') # Remove stop words


##############################################
# Read in our project-specific stop words list
##############################################

stop_words_file <- choose.files() # Select "StopWordList-ARI Project.txt"
our_stop_words <- readLines(stop_words_file) # Read it in

########################
### Actual cleaning part
#########################
dat$clean_text <- lapply(dat$clean_text, replace_non_ascii) # Change non-ascii characters like curly quote
dat$clean_text <- lapply(dat$clean_text, replace_contraction) # Remove contractions

# Lowercase and remove some non utf8 formatting
dat$clean_text <- tolower(dat$clean_text) #Make all text lower case
dat$clean_text <- lapply(dat$clean_text, utf8_normalize, map_quote = TRUE) #Get rid of the fancy quotes

# Remove some extra punctuation and formatting
dat$clean_text <- gsub('[[:punct:]]', ' ', dat$clean_text) # Remove punctuation
dat$clean_text <- gsub('…',' ', dat$clean_text) # Remove the fancy ellipses
#dat$clean_text <- removeNumbers(dat$clean_text) # Remove numbers

# Combine our list of stop words with a standard English stop word list
our_stop_words <- append(stopwords(kind = "en"), our_stop_words)
stop_words_regex <- paste(our_stop_words, collapse = '\\b|\\b') # Work-around that someone said helps with an error from tm package
stop_words_regex <- paste0('\\b', stop_words_regex, '\\b')



################
*Save for Later*
################

# Replace some Military acronyms
dat$clean_text <- gsub('AOCs','AOC ', dat$clean_text) # AOCs --> AOC
dat$clean_text <- gsub('NCOs','NCO ', dat$clean_text) # AOCs --> AOC
dat$clean_text <- gsub('AMI','Annual Military Inspection ', dat$clean_text) # AMI --> Annual Military Inspection
dat$clean_text <- gsub('OSI','Office of Special Investigations ', dat$clean_text) # OSI --> Office of Special Investigations
dat$clean_text <- gsub('AMT','Academy Military Trainer ', dat$clean_text) # AMT --> Academy Military Trainer


# Replace some words/contractions
dat$clean_text <- gsub('ole','old ', dat$clean_text) # ole --> old
dat$clean_text <- gsub('learnin','learning ', dat$clean_text) # learnin --> learning
dat$clean_text <- gsub('somethin','something ', dat$clean_text) # somethin --> something
dat$clean_text <- gsub('kinda','kind of ', dat$clean_text) # kinda --> kind of

# Replace some digits with words
dat$clean_text <- gsub('100','One Hundred ', dat$clean_text) # 100 --> One Hundred
dat$clean_text <- gsub('60','Sixty ', dat$clean_text) # 60 --> Sixty













