---
title: "Cleaning Notebook V2"
output: html_notebook
---

#############################
*Notebook to clean text data*
#############################

Need to clean text data for topic modeling analysis. Data acquired from transcribed interviews.


#######
*Setup*
#######

Install and load packages and select files for use (Local)

```{r}
#Opening Final Clean XLS
  library(readxl)
  dat.org <- read_xlsx("../../../Desktop/2.13 ARI Text.xlsx")
  dat <- dat.org
  
```

```{r}
# Install and load packages
#install.packages("tm")
#install.packages("utf8")
#install.packages("textclean")
library("utf8")
library("tm")
library("textclean")

# Choose file with a column of text to clean and load it in
#the_file <- choose.files()
#original_dat <- read.csv(the_file)
#colnames(original_dat)
```

#Creating New Column to Start Cleaning
```{r}
# Create and initialize new column to output our clean text to
dat$clean_text <- dat$Segment
dat$Segment[1]
```

##########################
*Removing All Punctuation*
##########################

#Remove all words inside [...]
```{r}
dat$clean_text <- gsub("\\[[^\\]]*\\]", " ", dat$clean_text, perl=TRUE, ignore.case=T)
dat$clean_text[c(1,2,3)]
```

#Remove \r
```{r}
dat$clean_text <- gsub("\r", " ", dat$clean_text, perl=TRUE, ignore.case=T)
dat$clean_text[c(1,2,30)]
```

#Remove \t
```{r}
dat$clean_text <- gsub("\t", " ", dat$clean_text, perl=TRUE, ignore.case=T)
dat$clean_text[c(1,2,50)]
```

#Remove \n
```{r}
dat$clean_text <- gsub("\n", " ", dat$clean_text, perl=TRUE, ignore.case=T)
dat$clean_text[c(25:30)]
```
#Remove \
```{r}
dat$clean_text <- gsub("\n", " ", dat$clean_text, perl=TRUE, ignore.case=T)
dat$clean_text[c(25:30)]
```

#Remove all words inside (...)
```{r}
dat$clean_text <- gsub("\\([^\\]]*\\)", " ", dat$clean_text, perl=TRUE, ignore.case=T)
dat$clean_text[203:206]

```

#########################
*Replacing Grammar Stuff*
#########################

# Replace the dashes in the text with a space (yes these are 3 DIFFERENT dashes)
```{r}
dat$clean_text <- gsub('—',' ', dat$clean_text) #Remove the long dashes
dat$clean_text <- gsub('–',' ', dat$clean_text) #Remove the dashes
dat$clean_text <- gsub('-',' ', dat$clean_text) #Remove the dashes

dat$clean_text[203:205]
```

# Replacing Contractions
```{r}
dat$clean_text <- lapply(dat$clean_text, replace_contraction) # Remove contractions
dat$clean_text[204:206]

```

# Replace the " in the text with a space (yes these are 3 DIFFERENT dashes)
```{r}
dat$clean_text <- gsub('—',' ', dat$clean_text) #Remove the long dashes
dat$clean_text <- gsub('–',' ', dat$clean_text) #Remove the dashes
dat$clean_text <- gsub('-',' ', dat$clean_text) #Remove the dashes

dat$clean_text[203:205]
```

#####################
*Remove MAXQDA Stuff*
#####################

#Interviewee
```{r}
dat$clean_text <- gsub("Female interviewee", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("emale interviewee", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("male interviewee", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("ale interviewee", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("le interviewee", " ", dat$clean_text, ignore.case=T)

#Remove those tricky "Interviewee"s that pop up
dat$clean_text <- gsub('Interviewee:', ' ', dat$clean_text, ignore.case = TRUE)

#Word
dat$clean_text <- gsub("Interviewee", " ", dat$clean_text, ignore.case = TRUE)
```

#nterviewee
```{r}
dat$clean_text <- gsub("Female nterviewee", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("emale nterviewee", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("male nterviewee", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("ale nterviewee", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("le nterviewee", " ", dat$clean_text, ignore.case=T)

#Remove those tricky "Interviewee"s that pop up
dat$clean_text <- gsub('nterviewee:', ' ', dat$clean_text, ignore.case = TRUE)

#Word
dat$clean_text <- gsub("nterviewee", " ", dat$clean_text, ignore.case = TRUE)
```

#erviewee
```{r}
dat$clean_text <- gsub("Female erviewee", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("emale erviewee", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("male erviewee", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("ale erviewee", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("le erviewee", " ", dat$clean_text, ignore.case=T)

#Remove those tricky "Interviewee"s that pop up
dat$clean_text <- gsub('erviewee:', ' ', dat$clean_text, ignore.case = TRUE)

#Word
dat$clean_text <- gsub("erviewee", " ", dat$clean_text, ignore.case = TRUE)
```

#Respondent
```{r}
dat$clean_text <- gsub("Female respondent", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("emale respondent", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("male respondent", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("ale respondent", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("le respondent", " ", dat$clean_text, ignore.case=T)

#Remove those tricky "Interviewee"s that pop up
dat$clean_text <- gsub('Respondent:', ' ', dat$clean_text, ignore.case = TRUE)

#Word
dat$clean_text <- gsub("Respondent", " ", dat$clean_text, ignore.case = TRUE)
```

#Participant
```{r}
dat$clean_text <- gsub("Female participant", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("emale participant", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("male participant", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("ale participant", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("le participant", " ", dat$clean_text, ignore.case=T)

#Word
dat$clean_text <- gsub("participant", " ", dat$clean_text, ignore.case = TRUE)

```

#Speaker
```{r}
dat$clean_text <- gsub("Female speaker", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("emale speaker", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("male speaker", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("ale speaker", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("le speaker", " ", dat$clean_text, ignore.case=T)


#Word
dat$clean_text <- gsub("Speaker", " ", dat$clean_text, ignore.case = TRUE)
```

#Numbers specific to Speaker
```{r}
dat$clean_text <- gsub("1:", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("2:", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("3:", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("4:", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("5:", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("6:", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("7:", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("8:", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("9:", " ", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("0:", " ", dat$clean_text, ignore.case=T)

```

#Colon
```{r}
dat$clean_text <- gsub(":", " ", dat$clean_text, ignore.case=T)
```

# Condense all the huge spaces to one
```{r}
dat$clean_text <- gsub("\\s+", " ", dat$clean_text)
head(dat$clean_text)

```


####################################
*Remove Verbal Stop Words (Not NLP)*
####################################

##########
Lower Case
##########

#mhmm
```{r}
dat$clean_text <- gsub("\\mhmmmmm.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\mhmmmm.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\mhmmm.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\mhmm.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\mhm.\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\mhmmmmm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\mhmmmm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\mhmmm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\mhmm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\mhm,\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\mhmmmmm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\mhmmmm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\mhmmm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\mhmm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\mhm\\b", "", dat$clean_text, ignore.case=T)
```

#hmm
```{r}
dat$clean_text <- gsub("\\hmmmmm.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\hmmmm.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\hmmm.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\hmm.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\hm.\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\hmmmmm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\hmmmm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\hmmm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\hmm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\hm,\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\hmmmmm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\hmmmm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\hmmm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\hmm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\hm\\b", "", dat$clean_text, ignore.case=T)
```

#umm
```{r}
dat$clean_text <- gsub("\\ummmmm.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\ummmm.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\ummm.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\umm.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\um.\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\ummmmm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\ummmm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\ummm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\umm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\um,\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\ummmmm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\ummmm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\ummm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\umm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\um\\b", "", dat$clean_text, ignore.case=T)
```

#mm
```{r}
dat$clean_text <- gsub("\\mmm.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\mm.\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\mmm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\mm,\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\mmm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\mm\\b", "", dat$clean_text, ignore.case=T)
```

#ah
```{r}
dat$clean_text <- gsub("\\ahhhhh.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\ahhhh.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\ahhh.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\ahh.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\ah.\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\ahhhhh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\ahhhh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\ahhh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\ahh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\ah,\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\ahhhhh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\ahhhh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\ahhh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\ahh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\ah\\b", "", dat$clean_text, ignore.case=T)
```

#Uh
```{r}
dat$clean_text <- gsub("\\uhhhhh.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\uhhhh.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\uhhh.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\uhh.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\uh.\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\uhhhhh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\uhhhh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\uhhh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\uhh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\uh,\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\uhhhhh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\uhhhh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\uhhh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\uhh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\uh\\b", "", dat$clean_text, ignore.case=T)
```

#oh
```{r}
dat$clean_text <- gsub("\\ohhhhh.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\ohhhh.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\ohhh.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\ohh.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\oh.\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\ohhhhh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\ohhhh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\ohhh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\ohh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\oh,\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\ohhhhh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\ohhhh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\ohhh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\ohh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\oh\\b", "", dat$clean_text, ignore.case=T)
```


##########
Upper Case
##########

#mhmm
```{r}
dat$clean_text <- gsub("\\Mhmmmmm.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Mhmmmm.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Mhmmm.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Mhmm.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Mhm.\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\Mhmmmmm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Mhmmmm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Mhmmm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Mhmm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Mhm,\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\Mhmmmmm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Mhmmmm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Mhmmm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Mhmm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Mhm\\b", "", dat$clean_text, ignore.case=T)
```

#hmm
```{r}
dat$clean_text <- gsub("\\Hmmmmm.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Hmmmm.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Hmmm.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Hmm.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Hm.\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\Hmmmmm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Hmmmm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Hmmm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Hmm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Hm,\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\Hmmmmm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Hmmmm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Hmmm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Hmm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Hm\\b", "", dat$clean_text, ignore.case=T)
```

#umm
```{r}
dat$clean_text <- gsub("\\Ummmmm.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Ummmm.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Ummm.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Umm.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Um.\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\Ummmmm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Ummmm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Ummm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Umm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Um,\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\Ummmmm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Ummmm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Ummm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Umm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Um\\b", "", dat$clean_text, ignore.case=T)
```

#mm
```{r}
dat$clean_text <- gsub("\\Mmm.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Mm.\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\Mmm,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Mm,\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\Mmm\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Mm\\b", "", dat$clean_text, ignore.case=T)
```

#ah
```{r}
dat$clean_text <- gsub("\\Ahhhhh.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Ahhhh.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Ahhh.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Ahh.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Ah.\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\Ahhhhh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Ahhhh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Ahhh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Ahh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Ah,\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\Ahhhhh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Ahhhh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Ahhh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Ahh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Ah\\b", "", dat$clean_text, ignore.case=T)
```

#uh
```{r}
dat$clean_text <- gsub("\\Uhhhhh.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Uhhhh.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Uhhh.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Uhh.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Uh.\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\Uhhhhh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Uhhhh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Uhhh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Uhh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Uh,\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\Uhhhhh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Uhhhh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Uhhh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Uhh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Uh\\b", "", dat$clean_text, ignore.case=T)
```

#oh
```{r}
dat$clean_text <- gsub("\\Ohhhhh.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Ohhhh.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Ohhh.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Ohh.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Oh.\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\Ohhhhh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Ohhhh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Ohhh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Ohh,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Oh,\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\Ohhhhh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Ohhhh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Ohhh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Ohh\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Oh\\b", "", dat$clean_text, ignore.case=T)
```


#############
*Wrapping-Up*
#############

#Remove Commas
```{r}
dat$clean_text <- gsub(",", " ", dat$clean_text)
dat$clean_text[350]
```
#Remove Spaces
```{r}
dat$clean_text <- gsub("\\s+", " ", dat$clean_text)
dat$clean_text[350]
```

#Remove Space at Beginning
```{r}
dat$clean_text <- gsub("^\\s", "", dat$clean_text)
dat$clean_text[350]
dat$clean_text[78]
```

#Remove Spaces
```{r}
dat$clean_text <- gsub("\\s+", " ", dat$clean_text)
dat$clean_text[350]
dat$clean_text[78]
```

###############
*Output to CSV*
###############

#Step 1 - Removing Normal Parts
```{r}
write.csv(dat, "2.13 ARI Cleaned Data (Step 1).csv")
```


#Step 2 - Removing Like & Just Words
```{r}
#Like
dat$clean_text <- gsub("\\Like.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Like,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Like\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\like.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\like,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\like\\b", "", dat$clean_text, ignore.case=T)


#Just
dat$clean_text <- gsub("\\Just.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Just,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\Just\\b", "", dat$clean_text, ignore.case=T)

dat$clean_text <- gsub("\\just.\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\just,\\b", "", dat$clean_text, ignore.case=T)
dat$clean_text <- gsub("\\just\\b", "", dat$clean_text, ignore.case=T)
```


### Explore the text 

```{r}
# Use tm package to create a corpus and explore the terms kept
corpus <- Corpus(VectorSource(dat$clean_text))
dtm <- DocumentTermMatrix(corpus)
tdm <- TermDocumentMatrix(corpus)

# Optionally remove terms that appear in <= 1% of documents
#tdm <- removeSparseTerms(tdm, .99)

# Looking at the 100 most frequent words
writeLines("~~~~~~~~~~ Most Frequent Terms ~~~~~~~~~~")
tdm$dimnames$Terms[1:100]

# Looking at the 100 least frequent words
writeLines("\n~~~~~~~~~~ Least Frequent Terms ~~~~~~~~~~")
tdm$dimnames$Terms[(tdm$nrow-100):tdm$nrow]
```


##########################################
#########################################
*Ignore (Jordan's NLP Code will do this)*

- The code I run references some widely used NLP package (I'm pretty sure)

#########################################
#########################################

# Read in our project-specific stop words list
stop_words_file <- choose.files() # Select "StopWordList-ARI Project.txt"
our_stop_words <- readLines(stop_words_file) # Read it in


# Remove some extra punctuation and formatting
dat$clean_text <- gsub('[[:punct:]]', ' ', dat$clean_text) # Remove punctuation
dat$clean_text <- gsub('…',' ', dat$clean_text) # Remove the fancy ellipses
#dat$clean_text <- removeNumbers(dat$clean_text) # Remove numbers

dat$clean_text <- stringr::str_replace_all(dat$clean_text, stop_words_regex, '') # Remove stop words


##############################################
# Read in our project-specific stop words list
##############################################

stop_words_file <- choose.files() # Select "StopWordList-ARI Project.txt"
our_stop_words <- readLines(stop_words_file) # Read it in

########################
### Actual cleaning part
#########################
dat$clean_text <- lapply(dat$clean_text, replace_non_ascii) # Change non-ascii characters like curly quote
dat$clean_text <- lapply(dat$clean_text, replace_contraction) # Remove contractions

# Lowercase and remove some non utf8 formatting
dat$clean_text <- tolower(dat$clean_text) #Make all text lower case
dat$clean_text <- lapply(dat$clean_text, utf8_normalize, map_quote = TRUE) #Get rid of the fancy quotes

# Remove some extra punctuation and formatting
dat$clean_text <- gsub('[[:punct:]]', ' ', dat$clean_text) # Remove punctuation
dat$clean_text <- gsub('…',' ', dat$clean_text) # Remove the fancy ellipses
#dat$clean_text <- removeNumbers(dat$clean_text) # Remove numbers

# Combine our list of stop words with a standard English stop word list
our_stop_words <- append(stopwords(kind = "en"), our_stop_words)
stop_words_regex <- paste(our_stop_words, collapse = '\\b|\\b') # Work-around that someone said helps with an error from tm package
stop_words_regex <- paste0('\\b', stop_words_regex, '\\b')



################
*Save for Later*
################

# Replace some Military acronyms
dat$clean_text <- gsub('AOCs','AOC ', dat$clean_text) # AOCs --> AOC
dat$clean_text <- gsub('NCOs','NCO ', dat$clean_text) # AOCs --> AOC
dat$clean_text <- gsub('AMI','Annual Military Inspection ', dat$clean_text) # AMI --> Annual Military Inspection
dat$clean_text <- gsub('OSI','Office of Special Investigations ', dat$clean_text) # OSI --> Office of Special Investigations
dat$clean_text <- gsub('AMT','Academy Military Trainer ', dat$clean_text) # AMT --> Academy Military Trainer


# Replace some words/contractions
dat$clean_text <- gsub('ole','old ', dat$clean_text) # ole --> old
dat$clean_text <- gsub('learnin','learning ', dat$clean_text) # learnin --> learning
dat$clean_text <- gsub('somethin','something ', dat$clean_text) # somethin --> something
dat$clean_text <- gsub('kinda','kind of ', dat$clean_text) # kinda --> kind of

# Replace some digits with words
dat$clean_text <- gsub('100','One Hundred ', dat$clean_text) # 100 --> One Hundred
dat$clean_text <- gsub('60','Sixty ', dat$clean_text) # 60 --> Sixty













